\section{Task 3: Dense Matrix Multiplication}
The code for this assignment can be found in the \textit{src/Task3} folder
handed in with this report. All functions (where applicable) have been templated
so the datatype contianed in the matrices can be any class \texttt{T}.

The code ships with a make file that supports the \texttt{clean},
\texttt{compile} and \texttt{run} targets. The current setup of the file will
run both GPU kernels on an assymetric matrix and compare to the CPU runs.

\subsection{Task 3.a: Sequential CPU Code}
The code for this task is mainly found in the \textit{cpuFunc.cu.h} file, like
earlier it contains a number of convinience functions as well as the
multiplication function \texttt{flatMatrixMultiply}.

\subsection{Task 3.c: Naive GPU Code}
The code for this task is found in the \textit{gpuFunc.cu.h} file, it contains
the same convinience functions as earlier, but the kernel is now replaced with
\texttt{flatNaiveMutliplyKernel}, which is a naive matrix multiplication kernel.

\subsection{Task 3.d: Tiled-Memory GPU Code}
The code for this task is found in the \textit{gpuFunc.cu.h} file, the
shared-memory kernel is implemented in the function
\texttt{flatSharedMultiplyKernel}.

\subsection{Execution Time}

Table \ref{tab:task3time} shows the running times of the CPU code and the
Shared-Memory GPU kernel. Time time is done for 10 runs of each method and the
time represents the average time for a single run. The times only cover the time
spent in the calulation kernels, and does not cover the overhead for copying
data to device memory.

\begin{table}
    \begin{tabular}{|r|r|r|r|}
        \hline
        \textbf{Matrix Dimensions} & \textbf{CPU Time} & \textbf{Naive GPU Time} & \textbf{Tiled-Memory GPU Time}\\\hline
        $(2\times 4)\times(4\times 3)$ & $>0\mu s$ & $38\mu s$ & $22\mu s$ \\
        $(40\times 10)\times(10\times 8)$ & $33\mu s$ & $20\mu s$ & $17\mu s$ \\

        $10 \times 10$ & $10\mu s$   & $17\mu s$  & $16\mu s$ \\
        $20 \times 20$ & $86\mu s$   & $27\mu s$  & $16\mu s$ \\
        $30 \times 30$ & $274\mu s$  & $73\mu s$  & $18\mu s$ \\
        $40 \times 40$ & $637\mu s$  & $103\mu s$ & $20\mu s$ \\
        $50 \times 50$ & $1229\mu s$ & $124\mu s$ & $20\mu s$ \\
        $60 \times 60$ & $2109\mu s$ & $145\mu s$ & $21\mu s$ \\ \hline

    \end{tabular}
    \caption{The running times for the CPU and GPU code as the average over 10
    runs.}
    \label{tab:task3time}
\end{table}

Table \ref{tab:task3time} shows that the CPU based code starts out slower than
both the GPU kernels, it also shows that the Tiled-memory kernel have a lower
execution time than the naive kernel.
